---
title: "E1: online candidate generation"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Imports

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggthemes)
library(tidyboot)
library(here)
library(jsonlite)
```

# 1. Qualitative results

## Examine example walks

```{r}
walks <- fromJSON('../data/lion-tiger-walks.json') %>% as_tibble()
```

# 2. Behavioral results

## Exclusions

```{r}
read_csv(here("data/exp1/e1_data_long.csv")) %>%
  group_by(clueGiverID, wordpair) %>%
  tally() %>%
  group_by(clueGiverID) %>%
  tally()
```

## How many clues listed?

```{r}
read_csv(here("data/exp1/e1_data_long.csv")) %>%
  group_by(clueGiverID, Level, wordpair) %>%
  tally() %>%
  ggplot(aes(x = n - 1)) +
    geom_bar() +
    theme_few() +
    labs(x = 'clues generated') +
    facet_grid(~ Level) +
    theme(aspect.ratio = 1)
```

## Individual differences? 

```{r}
read_csv(here("data/exp1/e1_data_long.csv")) %>%
  group_by(clueGiverID, Level, wordpair) %>%
  tally() %>%
  ggplot(aes(x = n - 1)) +
    geom_bar() +
    theme_few() +
    labs(x = 'clues generated') +
    facet_wrap(~ clueGiverID) +
    theme(aspect.ratio = 1/4)
```

# examine walk scores

```{r}
read_csv(here("data/exp1/scores.csv")) %>%
  gather(budget, value, union_2:intersection_8192) %>%
  mutate(Level = fct_relevel(Level, 'Easy', 'Medium', 'Hard')) %>%
  group_by(budget, Level) %>%
  tidyboot_mean(value,nboot=100) %>%
  separate(budget, into = c('strategy', 'budget')) %>%
  ggplot(aes(x = as.numeric(budget), y = log10(empirical_stat))) +
    geom_line(size=1, position = 'dodge') +
    geom_vline(xintercept = 64) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1, color = NA) +
    facet_grid(strategy ~ Level, scales = 'free') +
    theme_few() +
    scale_x_log10() +
    labs(x = 'budget', y = 'P(clue)')

ggsave("../analysis/plots/exp1_plot1.pdf", exp1_scores_plot)
```

# Examine how far you have to go to find clue

```{r}
indices = read_csv(here("data/exp1/indices.csv")) %>% 
  pivot_longer(names_to = 'key', values_to = 'value', 
               cols = c(starts_with('w1'), starts_with('w2'))) %>%
  separate(key, into = c('walk', 'i'), sep = '_index_walk') %>% 
  pivot_wider(names_from = "walk", values_from = "value") %>%
  mutate(union = reduce(across(w1:w2), pmin),
         intersection = reduce(across(w1:w2), pmax)) 

indices_permuted = read_csv(here("data/exp1/indices_permuted.csv")) %>% 
  pivot_longer(names_to = 'key', values_to = 'value', 
               cols = c(starts_with('w1'), starts_with('w2'))) %>%
  separate(key, into = c('walk', 'i'), sep = '_index_walk') %>% 
  pivot_wider(names_from = "walk", values_from = "value") %>%
  mutate(union = reduce(across(w1:w2), pmin),
         intersection = reduce(across(w1:w2), pmax)) 

num_clues <- indices %>%
  group_by(wordpair, clueGiverID, correctedClue) %>%
  tally() %>%
  group_by(wordpair, clueGiverID) %>%
  tally() %>%
  filter(n == 3)
  
bind_rows(
  indices %>% mutate(src = 'empirical'), 
  indices_permuted %>% mutate(src = 'permuted') 
) %>%
  #filter(intersection < 10000) %>%
  group_by(src, wordpair, Level, variable,clueGiverID, clueFinal, correctedClue) %>%
  summarize(intersection = mean(intersection), union = mean(union), w1 = mean(w1), w2 = mean(w2)) %>% arrange(wordpair, clueGiverID)
  # bind_rows(
  #   read_csv(here("data/exp1/indices_permuted.csv")) %>% 
  #     rename(union_index_permuted = union_index,
  #            intersection_index_permuted = intersection_index),
  #   read_csv(here("data/exp1/freq_scores.csv")), 
  #   read_csv(here("data/exp1/midpoint_scores.csv"))
  pivot_longer(names_to = 'measure', values_to = 'value', 
             cols = c(union, intersection, w1, w2)) %>% #  union_index_permuted, intersection_index_permuted, freq_index, mid_index
  mutate(Level = fct_relevel(Level, 'Easy', 'Medium', 'Hard')) %>%
  group_by(wordpair, measure, clueGiverID) %>%
  mutate(l = length(value))
  group_by(measure, src, variable, Level) %>%
  tidyboot_mean(value, nboot=100) %>%
  ggplot(aes(x = variable, y = empirical_stat, color = Level, linetype = src, group = interaction(Level, src))) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    facet_grid(measure ~ Level, scales = 'free') +
    scale_color_colorblind() +
    scale_x_discrete(guide = guide_axis(angle = 90)) +
    theme_few() +
    labs(x = '', y = 'first occurrence') 

ggsave("../analysis/plots/exp1_plot1.pdf", width = 10, height = 7, units = 'in')
```

```{r}
read_csv(here("data/exp1/indices.csv")) %>%
  ggplot(aes(x = intersection_index)) +
    geom_histogram() +
    theme_few()
```
# 

```{r}
read_csv(here("data/exp1/scores.csv")) %>%
  gather(budget, value, union_2:intersection_8192) %>%
  filter(clueFinal == Clue1) %>%
  mutate(Level = fct_relevel(Level, 'Easy', 'Medium', 'Hard')) %>%
  group_by(budget, Level) %>%
  tidyboot_mean(value>0.0001,nboot=100) %>%
  separate(budget, into = c('strategy', 'budget')) %>%
  ggplot(aes(x = as.numeric(budget), y = empirical_stat)) +
    geom_line(size=1, position = 'dodge') +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1, color = NA) +
    facet_grid(strategy ~ Level, scales = 'free') +
    ylim(0,1) +
    theme_few() +
    scale_x_log10() +
    labs(x = 'budget', y = '% visited at least once')
```



### MAY NOT NEED THESE EXTRA ANALYSES ###
# Examine lists of candidates

We compare the candidates generated by the models with the candidates generated by participants in a study.

```{r}
e1 = read_csv(here("data/exp1/e1_common_candidates.csv")) %>%
  mutate(Level = fct_relevel(Level, "easy", "medium","hard"))%>%
      mutate(budget = as.numeric(gsub("[^0-9.-]", "", budget)))
```

## overall common candidates

```{r}
common_candidates= e1 %>% rowwise()%>%
  mutate(prop_common_union = len_union_common/len_cluelist_behavioral,
    prop_common_intersection = len_intersection_common/len_cluelist_behavioral) %>%
  pivot_longer(names_to = "model", cols = prop_common_union:prop_common_intersection)%>%
  separate(model, into = c("prop", "index", "model")) %>% select(-c(prop,index))

e1plot = common_candidates %>% 
  group_by(Level, budget, model) %>%
  summarise(ci = list(mean_cl_boot(value) %>% 
                        rename(mean=y, lwr=ymin, upr=ymax))) %>% unnest%>%
ggplot(aes(x = budget, y = mean, color = model, group = model)) +
  geom_errorbar(aes(ymin=lwr, ymax=upr), size = 0.5, width=.2, 
                color = "gray", position = position_dodge(0))+
  geom_line()+
  geom_point(size = 2)+
  facet_wrap(~ Level)+
    labs(y = 'common candidates (proportion)', 
         title = "proportion of common candidates with behavioral data") +
  scale_color_calc()+
  theme_few() +
  theme(aspect.ratio = 1, legend.position = c(0.85, 0.2)) 

ggsave("../../analysis/plots/exp1_plot1.pdf", e1plot)

```

## final clue

```{r}
e1_finalclue = e1 %>% select(clueGiverID, Level, wordpair, clueFinal, 
                              budget, finalclue_index_union, finalclue_index_intersection) %>%
  pivot_longer(names_to = "model", cols = finalclue_index_union:finalclue_index_intersection) %>%
  separate(model, into = c("finalclue", "index", "model")) %>% select(-c(finalclue,index))%>%
  # set -1 to the lowest visitation frequency and take proportion for others
  # value == 1 means most visited node, value == 0 means not visited at all
  mutate(value = ifelse(value == -1, 0, (12218-value)/12218))

e1plot2 = e1_finalclue %>% 
  group_by(budget, model) %>%
  summarise(ci = list(mean_cl_boot(value) %>% 
                        rename(mean=y, lwr=ymin, upr=ymax))) %>% unnest%>%
  ggplot(aes(x = budget, y = mean, color = model, group = model)) +
  geom_errorbar(aes(ymin=lwr, ymax=upr), size = 0.5, width=.2, 
                color = "gray", position = position_dodge(0))+
  geom_line()+
  geom_point(size = 2)+
  labs(y = 'mean visitation proportion for final clue', 
       title = "proportion of final clue visitation") +
  theme_few() +
  scale_color_calc()+
  theme(aspect.ratio = 1, 
          legend.position = c(0.85, 0.2)) 
ggsave("../../analysis/plots/exp1_plot2.pdf", e1plot2)
```

