---
title: "Exp. 1: online candidate generation"
output: html_notebook
editor_options: 
  chunk_output_type: inline
---

# Imports

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)
library(tidyverse)
library(ggthemes)
library(tidyboot)
library(here)
library(jsonlite)
```

# 1. Qualitative results

## Vocab

```{r}
vocab <- read_csv(here('data/exp2/model_input/vocab.csv')) 

vocab %>%
  pull(Word) %>%
  length() %>%
  cat('words in vocab')
```

## Recode Levels

```{r}
d.raw.oldlevels <- read_csv(here("data/exp2/raw.csv")) %>%
  mutate(correct = str_detect(wordpair, fixed(tolower(GUESS_1_FINAL))) 
                   & str_detect(wordpair, fixed(tolower(GUESS_2_FINAL)))) %>%
  rowwise() %>%
  mutate(Word1 = min(target1, target2),
         Word2 = max(target1, target2)) %>% 
  ungroup() 

d.newlevels <- d.raw.oldlevels %>% 
  unite(wordpair, Word1, Word2, sep = '-') %>%
  group_by(wordpair) %>%
  summarize(correct = mean(correct)) %>%
  arrange(correct) %>%
  mutate(level = case_when(correct < .25 ~ 'Hard',
                           correct > .67 ~ 'Easy',
                           TRUE ~ 'Medium')) %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium', 'Hard'))

# preserve ordering of target pair in d.raw
d.levels <- bind_rows(
  d.newlevels %>% group_by(wordpair, level) %>% tally(),
  d.newlevels %>% 
    separate(wordpair, into = c('word1', 'word2'), sep = '-') %>%
    unite(wordpair, word2, word1, sep = '-') %>% 
    group_by(wordpair, level) %>% tally()
) %>% select(-n) %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium', 'Hard'))

d.raw <- d.raw.oldlevels %>%
  left_join(d.levels)
```

## Exclusions

```{r}
inclusions <- d.raw %>%
  group_by(clueGiverID, wordpair) %>%
  tally() %>%
  group_by(clueGiverID) %>%
  tally() %>% 
  filter(n > 20) %>%
  pull(clueGiverID)

d <- read_csv(here("data/exp2/cleaned.csv")) %>%
  filter(clueGiverID %in% inclusions) %>%
  select(-Level) %>%
  left_join(d.newlevels %>% select(wordpair, level)) %>%
  left_join(d.raw %>% select(clueGiverID, Word1, Word2, correct) %>% unique())
```

## How many clues listed?

```{r}
d %>%
  group_by(clueGiverID, level, wordpair) %>%
  tally() %>%
  ggplot(aes(x = n - 1)) +
    geom_bar() +
    theme_few() +
    labs(x = 'clues generated') +
    facet_grid(~ level) +
    theme(aspect.ratio = 1)
```

## Individual differences? 

Most games stuck to exactly 3 clues but some were way out there.

```{r}
d %>%
  group_by(clueGiverID, level, wordpair) %>%
  tally() %>%
  group_by(clueGiverID) %>%
  mutate(avg_num_clues = mean(n)) %>%
  mutate(clueGiverID = as.character(clueGiverID)) %>%
  ggplot(aes(x = n - 1)) +
    geom_bar() +
    theme_few() +
    labs(x = 'clues generated') +
    facet_wrap(~ fct_reorder(clueGiverID, avg_num_clues)) +
    theme(aspect.ratio = 1/4)
```

# 2. Behavioral results

## 2.1 Manipulation check

```{r}
ggplot(d.newlevels, aes(x = correct*100, fill = level)) +
    geom_histogram(bins = 20) +
    geom_vline(xintercept = c(66, 25)) +
    labs(x = '% correct') +
    theme_few() +
    scale_fill_manual(values = c('#60BD68', '#D8CF23', '#CC253D'))

ggsave(here('analysis/plots/difficulty_dist.pdf'), units = 'in', width = 7, height = 4)
```

```{r}
d.raw %>% group_by(level) %>% tidyboot_mean(correct, nboot = 1) 
```

```{r}
d.raw %>% group_by(level) %>% tidyboot_mean(TEOption1, nboot = 1000, na.rm = T) %>% 
  ggplot(aes(x = level, y = empirical_stat, fill = level)) +
    geom_bar(stat = 'identity') +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    labs(y = 'time to generate first clue (ms)') +
    theme_few() +
    scale_fill_few() +
    theme(aspect.ratio = 1, legend.position = 'none') +
    scale_fill_manual(values = c('#60BD68', '#D8CF23', '#CC253D'))

ggsave(here('analysis/plots/generation_time.pdf'), units = 'in', width = 4, height = 4)
```

```{r}
d.raw %>%
  lm(TEOption1 ~ level, data = .) %>%
  summary()
```

## 2.2: Order effects

```{r}
d.order <- d %>%
  filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  spread(seqOrder, correctedClue) %>%
  gather(seqOrder, correctedClue, starts_with('clueOption')) %>%
  mutate(match = clueFinal == correctedClue) %>%
  ungroup() %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium')) 

d.order %>%
  group_by(seqOrder, level) %>%
  summarize(m = mean(match, na.rm = T)) %>%
  spread(seqOrder, m) %>%
  mutate(other = 1 - clueOption1 - clueOption2 - clueOption3) %>%
  gather(seqOrder, m, -level) %>%
  ggplot(aes(x = level, y = m, fill = seqOrder)) +
    geom_bar(stat = 'identity', color = 'black') +
    theme_few() +
    scale_fill_grey(name = "order", start=1, end=0.2) +
    labs(y = 'proportion matching final clue', x = '') +
    theme(aspect.ratio = 1)

ggsave(here('analysis/plots/order.pdf'), units = 'in', width = 4, height = 3)
```

```{r}
d.order %>%
  group_by(seqOrder) %>%
  summarize(m = mean(match, na.rm = T))
```

```{r}
d.order %>%
  group_by(seqOrder, level) %>%
  summarize(m = mean(match, na.rm = T)) %>%
  spread(seqOrder, m) %>%
  mutate(other = 1 - clueOption1 - clueOption2 - clueOption3) %>% arrange(-clueOption1)
```

```{r}
library(lme4)
d.order %>%
  filter(seqOrder == 'clueOption1') %>%
  glmer(match ~ level + 
               (1 + level | clueGiverID) ,
        data = ., 
        family = 'binomial') %>%
  summary()
```

```{r}
d.order %>%
  glmer(match ~ seqOrder + 
               (1 + seqOrder | clueGiverID) ,
        data = ., 
        family = 'binomial',
        contrasts = list(seqOrder = contr.treatment(3, base = 2))) %>%
  summary()
```

## Associated with accuracy?

```{r}
d.order %>% 
  group_by(seqOrder, level, correct) %>%
  summarize(m = mean(match, na.rm = T)) %>%
  arrange(level, correct) %>%
  spread(seqOrder, m) %>%
  mutate(other = 1 - clueOption1 - clueOption2 - clueOption3) %>%
  gather(seqOrder, m, -level, -correct) %>%
  ggplot(aes(x = correct, y = m, fill = seqOrder, color = level)) +
    geom_bar(stat = 'identity', position = 'stack') +
    theme_few() +
    facet_grid(~ level) +
    scale_color_manual(values = c('#60BD68', '#D8CF23', '#CC253D')) +
    scale_fill_grey(name = "order", start=1, end=0.2) + 
    labs(y = '% selected as clue', x = 'accuracy') +
    theme(aspect.ratio = 2, legend.position = 'none') +
    ylim(0,1)

ggsave(here('analysis/plots/exp2_order_difficulty.pdf'), 
       units = 'in', width = 4.5, height = 3)
```

```{r}
d.order %>% 
  group_by(seqOrder, level, match) %>%
  tidyboot_mean(correct, na.rm = T) %>%
  filter(match) %>%
  arrange(level) %>%
  ggplot(aes(x = seqOrder, y = empirical_stat, color = level, group = level)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_few() +
    scale_color_few(name = "order") +
    labs(y = 'accuracy', x = 'selection') +
    theme(aspect.ratio = 1) +
    ylim(0,1)
```

## Frequency differences?

Something weird is going on with Medium, but across the board, it looks like the final clue is less common than the ones in the list. 

```{r}
d %>% filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  left_join(vocab %>% rename(correctedClue = Word, freq= LgSUBTLWF), by = "correctedClue") %>%
  group_by(seqOrder, level) %>%
  tidyboot_mean(freq, na.rm = T) %>%
  ggplot(aes(x = seqOrder, y = empirical_stat, color = level, group = level)) +
    geom_point() +
    geom_line() +
    geom_errorbar(aes(ymin = ci_lower, ymax = ci_upper), width = 0) +
    theme_few() +
    scale_fill_colorblind(name = "order") +
    labs(y = 'proportion matching final clue', x = 'difficulty') +
    theme(aspect.ratio = 1)
```

Statistics

```{r}
library(lmerTest)
d %>% filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  left_join(vocab %>% rename(correctedClue = Word, freq= LgSUBTLWF), by = "correctedClue") %>%
  lmer(freq ~ seqOrder + (1 | clueGiverID),
       data = .) %>%
  summary()
```

# 3. Model results

## Examine example walks

```{r}
pairs = d %>% pull(wordpair) %>% unique()
clues <- read_csv(here('data/exp2/cleaned.csv')) %>%
  group_by(wordpair, seqOrder, correctedClue) %>%
  tally(name = 'clueCount') 

getWalks <- function(pair) {
  paste0('data/exp2/model_output/', pair, '-walks.json', collapse = '') %>%
    here() %>%
    fromJSON() %>% 
    as_tibble() %>%
    mutate(step = row_number()) %>%
    gather(walk, correctedClue, -step) %>%
    mutate(walk = gsub('walk-', '', walk),
           start = ifelse(as.integer(walk) %% 2 == 0, 'w1', 'w2')) %>% 
    right_join(clues %>% filter(wordpair == pair), by = c('correctedClue')) %>%
    group_by(walk, correctedClue, wordpair) %>%
    select(-start) %>%
    filter(step == first(step)) %>%
    group_by(step, correctedClue, wordpair) %>%
    tally() %>%
    ungroup() %>%
    group_by(wordpair) %>%
    complete(correctedClue, step = min(step):max(step), fill = list(n=0)) %>%
    group_by(correctedClue, wordpair) %>%
    mutate(cdf = cumsum(n)/2000) %>%
    return()
}

bind_rows(
  getWalks('bat-bounce'),
  getWalks('trauma-weird')
) %>%
  left_join(clues) %>%
  ggplot(aes(x = step, y = cdf)) +
    geom_line(aes(group = correctedClue, alpha = clueCount)) +
    geom_text(aes(label = correctedClue), check_overlap = F,
              data = . %>% filter(clueCount > 10, step == 9990)) +
    theme_few() +
    facet_wrap(~ wordpair) +
    scale_x_log10(limits = c(2,20000))

ggsave(here(paste0('analysis/plots/cdf-duo.pdf')), units='in', height = 4, width = 8)
```

Statistics

```{r}
# note that this will take a very long time! 
walks <- map(pairs, getWalks, .progress = T) %>%
  list_rbind() 

d.spearmancor <- walks %>%
  left_join(clues) %>%
  filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  group_by(wordpair, seqOrder, step) %>%
  summarize(r = cor(cdf, clueCount, method = 'spearman')) %>%
  left_join(d.levels) 

d.spearmancor.toplot <- d.spearmancor %>%
  ungroup() %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium', 'Hard')) %>%
  group_by(step, seqOrder, level) %>%
  summarize(ci_lower = mean(r) - 2*sd(r)/sqrt(length(r)),
            ci_upper= mean(r) + 2*sd(r)/sqrt(length(r)),
            r = mean(r)) 

d.spearmancor.toplot %>%
  ungroup() %>%
  mutate(seqOrder = fct_relevel(seqOrder, 'clueOrder2', 'clueOrder1', 'clueOrder3', 'clueFinal')) %>%
  ggplot(aes(x = step, y = r, alpha = seqOrder, color = level)) +
    # geom_line(aes(group = wordpair), alpha = 0.1, 
    #           data = d.spearmancor  %>% filter(step %in% 2**seq(1,13))) +
    geom_line() +
    theme_few() +
    scale_color_manual(values = c('#60BD68', '#D8CF23', '#CC253D')) +
    facet_grid(~ level)+
    scale_alpha_manual(values = c(1, .2, .4, .8)) +
    labs(y = 'spearman correlation') +
    scale_x_log10() +
    theme(aspect.ratio = 1)

ggsave(here('analysis/plots/exp2-spearman-broken-out.pdf'), units = 'in', width = 8, height = 4)
```

```{r}
d.spearmancor %>% group_by(step, level) %>% summarize(r = mean(r)) %>% group_by(level) %>% filter(r == max(r)) 
```

## Examine how far you have to go to find clue

Find best alpha overall

```{r}
df.mixture <- read_csv(here("data/exp2/model_output/mixture_scores.csv")) %>% 
  select(-Level) %>%
  left_join(d.levels) %>%
  mutate(seqOrder = fct_relevel(seqOrder, 'clueFinal', after = 3)) %>%
  filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  group_by(level, seqOrder, alpha) %>%
  summarize(mix = mean(mixture_index, na.rm=T))  %>%
  group_by(level, seqOrder) %>%
  filter(mix == min(mix))
```


```{r}
bind_rows(
  read_csv(here("data/exp2/model_output/ranks.csv"))  %>% mutate(src = 'empirical'),
  read_csv(here("data/exp2/model_output/ranks_permuted.csv")) %>% mutate(src = 'permuted')
) %>%
  left_join(read_csv(here("data/exp2/model_output/freq_scores.csv")) %>% mutate(src = 'empirical'), 
            by = c('clueGiverID', 'correctedClue', 'seqOrder', 'Level', 'src', 'wordpair')) %>% 
  left_join(read_csv(here("data/exp2/model_output/mixture_scores.csv")) %>% 
              mutate(src = 'empirical')  %>% filter(alpha == 1.0), 
            by = c('clueGiverID', 'correctedClue', 'seqOrder', 'Level', 'src', 'wordpair')) %>%
  filter(correctedClue %in% (vocab %>% pull(Word))) %>%
  select(-Level) %>%
  left_join(d.levels) %>%
  mutate(seqOrder = fct_relevel(seqOrder, 'clueFinal', after = 3)) %>%
  filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  group_by(src, wordpair, level, seqOrder,clueGiverID, correctedClue) %>%
  summarize(intersection = mean(intersection), 
            union = mean(union), 
            single = mean(c(w1_index_walk, w2_index_walk)),
            freq = mean(freq_index),
            mix = mean(mixture_index)) %>% 
  pivot_longer(names_to = 'measure', values_to = 'value', 
               cols = c(union, intersection, single, mix, freq)) %>% 
  ungroup() %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium', 'Hard')) %>%
  mutate(measure = fct_relevel(measure, 'freq', 'mix', 'single','union', 'intersection')) %>%
  group_by(measure, seqOrder, src, level) %>%
  filter(!is.na(value)) %>%
  tidyboot_mean(value, nboot=10, na.rm = T) %>%
  ggplot(aes(x = seqOrder, y = empirical_stat, color = level, linetype = src, group = interaction(src, level))) +
    geom_line(aes(alpha =)) +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1, color = NA) +
    facet_grid( ~ measure) +
    scale_color_manual(values = c('#60BD68', '#D8CF23', '#CC253D')) +
    scale_x_discrete(guide = guide_axis(angle = 90)) +
    theme_few() +
    scale_y_log10(limits=c(100,NA)) +
    labs(x = '', y = 'first occurrence') +
    theme(aspect.ratio = 2)

ggsave("../analysis/plots/exp2_ranks.pdf", width = 6, height = 4, units = 'in')
```

## Examine mixture scores

```{r}
read_csv(here("data/exp2/model_output/mixture_scores.csv")) %>% 
  mutate(src = 'empirical')%>%
  select(-Level) %>%
  left_join(d.levels) %>%
  mutate(seqOrder = fct_relevel(seqOrder, 'clueFinal', after = 3)) %>%
  group_by(src, wordpair, level, seqOrder,clueGiverID, correctedClue, alpha) %>%
  summarize(mix = mean(mixture_index)) %>% 
  summarize(value = min(value, na.rm = T))
  filter(seqOrder %in% c('clueOption1', 'clueOption2', 'clueOption3', 'clueFinal')) %>%
  pivot_longer(names_to = 'measure', values_to = 'value', 
               cols = c(mix)) %>% 
  ungroup() %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium', 'Hard')) %>%
  group_by(measure, seqOrder, src, level) %>%
  tidyboot_mean(value, nboot=10, na.rm = T) %>%
  ggplot(aes(x = seqOrder, alpha = alpha, y = empirical_stat, color = level, linetype = src, group = interaction(src, alpha, level))) +
    geom_line() +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1, color = NA) +
    #facet_grid( ~ level) +
    scale_color_few() +
    #scale_x_discrete(guide = guide_axis(angle = 90)) +
    theme_few() +
    scale_y_log10(limits=c(100,NA)) +
    labs(x = 'alpha', y = 'first occurrence') +
    theme(aspect.ratio = 2)

ggsave("../analysis/plots/exp2_ranks_mixture.pdf", width = 6, height = 4, units = 'in')
```

## Examine walk scores

```{r}
d.scores <- bind_rows(
  read_csv(here("data/exp2/model_output/scores.csv")) %>% mutate(src = 'empirical'),
  read_csv(here("data/exp2/model_output/scores_permuted.csv")) %>% mutate(src = 'permuted')
) %>%
  filter(seqOrder %in% c('clueFinal', 'clueOption1', 'clueOption2', 'clueOption3')) %>%
  gather(budget, value, union_2:w2_8192) %>%
  separate(budget, into = c('strategy', 'budget')) %>% 
  filter(strategy != 'freq') %>%
  mutate(strategy = fct_collapse(strategy, single = c('w1', 'w2'))) %>%
  select(-Level) %>%
  left_join(d.levels) %>%
  mutate(level = fct_relevel(level, 'Easy', 'Medium', 'Hard')) %>%
  group_by(budget, src, level, strategy) %>%
  summarize(empirical_stat = mean(value, na.rm = T), 
            ci_upper = empirical_stat + 2 * sd(value, na.rm=T)/sqrt(length(value)),
            ci_lower = empirical_stat - 2 * sd(value, na.rm=T)/sqrt(length(value))
  ) 

d.scores %>%
  ggplot(aes(x = as.numeric(budget), y = empirical_stat, color = level, linetype = src, group = interaction(src, level))) +
    geom_line(size=1, position = 'dodge') +
    geom_ribbon(aes(ymin = ci_lower, ymax = ci_upper), alpha = 0.1, color = NA) +
    facet_grid( ~ strategy, scales = 'free') +
    theme_few() +
    scale_color_few()+
    scale_x_log10() +
    labs(x = 'budget', y = 'P(visit)') +
    theme(aspect.ratio = 2)

ggsave("../analysis/plots/exp2_scores.pdf", width = 6, height = 4, units = 'in')
```
